Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
sda

\section{Introduction}
%API Design (and a little bit of ecosystems, and a bit of problem statement)
As the software industry and the open source movement steadily grow, the number of public APIs is increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}. The main reason is that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}. 
%software evolution 
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.

@@

@@

Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.

@@

\subsection{Data Collection}
The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of the same API which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API.

From the APIs we collected data about method names, parameters and return types. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. The collected data were input into tables and spreadsheets, according to the API version. From the archival documentation we collected data regarding the motive behind the functionality in API calls. Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.

@@

First degree interviews were also conducted after the initial source code inspections had taken place. The main purpose of these was to validate our findings with the architects of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the architects of the APIs was to provide further insight of the users of the API.

@@

\subsection{Validity Threats}
% This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.

>>>>

%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.

\section{Introduction}
%API Design (and a little bit of ecosystems, and a bit of problem statement)
As the software industry and the open source movement steadily grow, the number of public APIs is increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}. The main reason is that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}. 
%Software Evolution 
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.

@@

\subsection{Background}

\subsubsection{API}

\subsubsection{Software Evolution}

\subsubsection{Software Ecosystems}

\subsection{Related Work}

@@

@@

\subsection{Data Collection}
The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of the same API which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API.

From the APIs we collected method names, parameters and return types. (Additional data will collected. This is just an initial ``estimation" for the proposal). The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. The collected data were input into tables and spreadsheets, according to the API version. From the archival documentation we collected data regarding the motive behind the functionality in API calls. Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.

@@

Interviews were also conducted after the initial source code inspections had taken place. The main purpose of these was to validate our findings with the architects of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the architects of the APIs was to provide further insight of the users of the API.

@@

\subsection{Validity Threats}
% This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
This section has been structured around a well-known schema used for classifying validity threats \cite{runeson2009guidelines}.
